Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-28 paper/high-assurance-contracts.tex
Fix label on the monitor contract

    eq policy : bool = (rsp => req) ->
                         (    (isPending => latency < MAX_LATENCY)
                          and (rsp => (req or pre(isPending))));
    *\label{line:mon-policy}*
    -- stop user definitions

>>>>

    eq policy : bool = (rsp => req) -> *\label{line:mon-policy}*
                         (    (isPending => latency < MAX_LATENCY)
                          and (rsp => (req or pre(isPending))));
    -- stop user definitions
